Privacy-Respecting Type Error Telemetry at Scale

### 2023-12-12 programming23/paper.tex
units on plots
grant++ diff cmd

This telemetry design is admittedly coarse-grained.
For instance, it does not distinguish between edits that remove one error
while introducing another.
We acknowledge this and other threats in~\cref{s:threats}.
The main advantages of this telemetry are the small size of each record and
the complete lack of private information.
Furthermore, despite the limitations, this telemetry supports a variety of
inferences that we showcase in the next section.

@@

\Cref{f:records-per-hour} provides a time-ordered distribution of the data.
The x-axis is labeled with a California time zone; the thin vertical lines
mark the start of a new day.
For each of the 24 hours in each day, there is one blue bar
indicating the number of records generated during that hour.
Each hour has a few dozen to over 3,000 records, typically about
1,000.
We conjecture the very low bars are due to outage on
the logging server and that the very tall bars are due to
user scripts that generated a huge number of keystrokes.
%% TODO investigate one tower, what's happening?? all one session?
Telemetry ended in early April; however, there are short bars in the mid-April
range from developers who waited a few days to update Roblox Studio.

@@

  \mstrict{}
  \includegraphics[width=\columnwidth]{img/error-count-strict-row--te-density-diff-no-switch.pdf}
  \caption{Changes in type error density ($\frac{\mbox{\#errors}}{\mbox{\#lines}}$) over time (seconds).}
  \label{f:error-density}
\end{figure}

@@

Thanks to Benjamin Chung for several helpful discussions about data analysis
and effective plotting.
Greenman was supported by
NSF grant \href{https://nsf.gov/awardsearch/showAward?AWD_ID=2030859&HistoricalAwards=false}{2030859}
to the CRA for the \href{https://cifellows2020.org}{CIFellows} project.

>>>>

This telemetry design is admittedly coarse-grained.
For instance, it does not distinguish between edits that
ignore a type error from edits that remove one error
while introducing another.
We acknowledge this and other threats in~\cref{s:threats}.
The main advantages of this telemetry are the small size of each record and
the complete lack of private information.
Furthermore, despite the limitations, this telemetry supports a variety of
inferences that we showcase in the next section.

@@

\Cref{f:records-per-hour} provides a time-ordered distribution of the data.
The x-axis is labeled with a California time zone; the thin vertical lines
mark the start of a new day.
For each of the 24 hours in each day, there is one blue bar
indicating the number of records generated during that hour.
Each hour has a few dozen to over 3,000 records, typically about
1,000.
We conjecture the very low bars are due to outage on
the logging server and that the very tall bars are due to
user scripts that generated a huge number of keystrokes.
%% two biggest towers (7050 6691) are mostly from 2 sessions:
%% (("\"178,020,742,609,772\"" . 6079))
%% (("\"458,983,252,701,986\"" . 5085))
Telemetry ended in early April; however, there are short bars in the mid-April
range from developers who waited a few days to update Roblox Studio.

@@

  \mstrict{}
  \includegraphics[width=\columnwidth]{img/error-count-strict-row--te-density-diff-no-switch.pdf}
  \caption{Changes in type error density ($\frac{\mbox{\#curr - \#old errors}}{\mbox{\#lines}}$) over time (seconds).}
  \label{f:error-density}
\end{figure}

@@

Thanks to Benjamin Chung for several helpful discussions about data analysis
and effective plotting.
We gratefully acknowledge support from
NSF grant \href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=2227863&HistoricalAwards=false}{SHF-2227863}
and NSF grant \href{https://nsf.gov/awardsearch/showAward?AWD_ID=2030859&HistoricalAwards=false}{2030859}
to the CRA for the \href{https://cifellows2020.org}{CIFellows} project.
